\documentclass{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts, booktabs, hyperref, graphicx, float, esint, xcolor, subcaption, xspace}
\usepackage[margin=1.0in]{geometry}
% mathbbol, causing errors
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{0pt}

\newcommand{\vr}{\vec{r}}
\newcommand{\vOmega}{\vec{\Omega}}
\newcommand{\vJ}{\vec{J}}
\newcommand{\vO}{\vec{\Omega}}
\newcommand{\bra}{\left\langle}
\newcommand{\ket}{\right\rangle}
\newcommand{\sbra}{\left[}
\newcommand{\sket}{\right]}
\renewcommand{\div}{\vec{\nabla} \cdot}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\vbeta}{\vec{\beta} }
\newcommand{\pdx}{\frac{\partial}{\partial x}}
\newcommand{\pdy}{\frac{\partial}{\partial y}}
\newcommand{\pdz}{\frac{\partial}{\partial z}}
\newcommand{\intrrr}{\int d^3 r \,}
\newcommand{\intrr}{\int d^2 r \,}
\newcommand{\dEdphi}{\partial_\phi E }
\newcommand{\dEdp}{\partial_p E }
\newcommand{\dBdphi}{\partial_\phi B }
\newcommand{\dBdp}{B }
\newcommand{\adj}{\phi^\dag}
\newcommand{\surf}{\int_{\partial V}}
\newcommand{\domain}{V}
\newcommand{\bound}{\partial V}
\newcommand{\vn}{\vec{n}}
\newcommand{\Edd}{\mathbb{E}}
\newcommand{\BEdd}{B}
\newcommand{\sigt}{\sigma_t}
\newcommand{\sigs}{\sigma_s}
\newcommand{\siga}{\sigma_a}
\newcommand{\isigt}{c}
% why \newcommand{\angSource}{q_\Omega}
\newcommand{\angSource}{q}
\newcommand{\scalSource}{q}
\newcommand{\angResp}{q^\dag}
\newcommand{\scalResp}{q^\dag}
\newcommand{\qoi}{{\it QoI}\xspace}
\newcommand{\Ui}{U_i}
\newcommand{\Uipo}{U_{i+1}}
\newcommand{\Uimo}{U_{i-1}}
\newcommand{\Uo}{U_o}
\newcommand{\Uopo}{U_{o+1}}
\newcommand{\Uomo}{U_{o-1}}




\begin{document}
\begin{center}
Ian Halvic \\
TODO\\
\end{center}

\section{To Do}
This to revise of Thesis between presentation and submission.
\begin{itemize}
\item Revise aVET formulation to explain why it cannot be used with boundary incident. Extend this correction to the results. Remove from most graphs where this method should not apply. 
\item Revise the axes of most graphs, change to show $\%$ values instead of the decimal values shown now.
\item Rework some of the colors on the sensitivity graphs to make them more distinct.
\item For flux graphs, plot using appropriately spaced markers because lines are frequently overlaid.
\item For Reed problem section in thesis, change to focus on the two QoI regions (there the void QoI experiences issues with VET). Focus discussion of this problem on this. Include term by term breakdown as was in presentation.
\item Add in summary table methods/inner-products used , as was shown in presentation. Maybe a quick summary blurb on each for expected behavior.
\item Quick section on response perturbation $\delta q^\dag$ in forward problems, and why it is straightforward for most methods.
\item Add better titles to the graphs because review will likely complain about that it seems.
\item In some test cases, show the plots of the perturbed flux for some select perturbations. Along with this show the $\delta \Edd$ plots where needed.
\item Make sure no equations are going past margins, there may be a case of this or two. 
\end{itemize}

\end{document}